---
title: "Easy themes for your plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Easy themes for your plots}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

<style>
    img {
        border: 0;
    }
</style>

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

## Configuration

Before using this package you'll want to configure color codes and palette combinations. This is accomplished on the ```R/config.yml``` file using standard yaml formatting (including a trailing newline). This needs to be performed the package is installed. Required components are:

1. colors: define hex codes that correspond to specific hex color codes. If you're looking for inspiration there are plenty of [tools to help](https://coolors.co/f58220-7ac143-591f00-ffd051-f7a964-61ab33-b84000-ffe499). These will provide both the basis for palettes you define but also be available to use manually.
2. palettes: named collections of colors defined in the colors section. We minimally require a *main* palette and support as many more as desired.

```
colors:
  orange: "#F58220"
  lime: "#7AC143"
  brown: "#591F00"
  gold: "#ffd051"
  sand: "#f7a964"  
  green: "#508d2a"
  red: "#b84000"
  cream: "#b84000"
palettes:
  all:
    - orange
    - lime
    - brown
    - green
    - gold
    - red
  main:
    - orange
    - lime  
  light:
    - orange
    - gold

```

## Quick start

These examples demonstrate usage of two functions (scales) that can be used to modify color schemes of a ggplot. Common params for these include:

- __*palette*__ Name of a configured palette of colors
- __*reverse*__ Boolean if you want to reverse the order of configured colors
- __*discrete*__ Boolean indicating whether color aesthetic is discrete. Alternatively it will create a scale appropriate for continuous values.

```{r fig.width=6}
library(EasyBranding)
library(ggplot2)
library(ggprism)

theme_set(theme_prism() + theme(aspect.ratio = 0.4))
p <- ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color = Species)) +
  geom_point(size = 2) +
  geom_smooth(formula = 'y ~ x', method = 'glm', se = F)

p + scale_color_brand() + 
  labs(title='main palette')
p + scale_color_brand(palette = 'dark') + 
  labs(title='dark palette')
p + scale_color_brand(reverse = T) +
  labs(title='reverse main palette')
```

In this series we demonstrate how palettes are created when datasets require more colors than those defined in a palette. This is typically accomplished by interpolating intermediate values, therefore when a palette is defined by 2 values the colors are all intermediate those two, then more are specified then colors are interpolated along those specifications.

```{r fig.width=6}
df <- data.frame(category = LETTERS[1:20],
                 value = runif(20)+1)
p <- ggplot(df, aes(category, value, fill = category)) +
  geom_col()
p + scale_fill_brand() + 
  labs(title='main palette') +
  theme(legend.position = 'none')
p + scale_fill_brand(palette = "all") + 
  labs(title='*all* palette') +
  theme(legend.position = 'none')
```
